Uniform formula lower bounds for testing the existence of and counting satisfiable assignments

### 2022-06-26 article/main.tex
Added defs to intro, done

\subsection{Uniform formulas}
A boolean formula $\phi$ over $n$ inputs is a 
rooted full binary tree\footnote{\textit{Full} means that every node has either two or zero children.}
whose internal nodes, called gates, are labeled by a function $f: \bit^2 \rightarrow \bit$,
and leaves are labeled with a variable, $x_i$ its negation $\neg x_i$ for some $i, 1\le i \le n$,
or a constant $c\in\bit$.
The depth of a formula is the depth of the underlying tree.

@@

\todoh{To introduce: family of formulas computing a language}
% In this work, we focus on formulas with depth $d(n) = (c + o(1))\log n$, for some $c > 1$.
However, there exists formulas of \textit{constant} depth that compute undecidable languages.
In this work, we restrict our attention to uniform formulas, 
that is family of formulas for which the description of the
$n$-input formula can be computed efficiently.
We first recall a usual definition of uniform formulas.
\begin{definition}[``Usual'' polylog-time uniform formulas]
	A family of formulas $(\varphi_n)_{n \ge 1}$ of depth $(c + o(1))\log n$ 
	is \textit{polylog-time uniform} if there exists a machine $A_\varphi$
	such that for every $n$ and every $b\in\bit^{\leq (c + o(1))\log n}$,
	$A_\varphi(b, n)$ outputs a description of the gate at position $b$ in $\varphi_n$ in time $\log^{O(1)} n$.
\end{definition}

@@

\subsection{Details of the model}
\todoh{describe model}
\todoh{link to code?}

>>>>

\subsection{Uniform formulas}
A boolean formula $\phi$ over $n$ inputs is a 
rooted full binary tree\footnote{\textit{Full} means that every node has either two or zero children.}
whose internal nodes, called gates, are labeled by a function $f: \bit^2 \rightarrow \bit$,
and leaves are labeled with a variable, $x_i$ its negation $\neg x_i$ for some $i, 1\le i \le n$,
or a constant $c\in\bit$.
The depth of a formula is the depth of the underlying tree.
Given an input $x \in\bit^n$, the value of $\phi$ at $x$ can be defined 
as the value of it root on input $x$, 
where the value of a gate is defined inductively as follows:
\[val(g) =\begin{cases}
	c & \text{ if $g$ is labeled with the constant} c\in\bit\\
	x_i & \text{ if $g$ is labeled with $x_i$}\\
	\neg x_i & \text{ if $g$ is labeled with $\neg x_i$}\\
	f(g_1, g_2) & \text{ if $g$ is labeled  $f$, and $g_1,g_2$ are children of $g$}
\end{cases}\]

@@

A family of formulas is a sequence $(\phi_n)_{n\in\NN}$ of formulas such that
for every i, $\phi_i$ is a formula over $i$ inputs.
A language $L\subseteq \bit^*$
is computed by\footnote{In what follows, we may use ``$L$ has formulas ...'' for ``$L$ is computed by a family of formulas ...''} 
the family of formulas $(\phi_n)_{n\in\NN}$
if for every $n$ and every $x\in\bit^n$, $\phi_n(x) = 1 \Leftrightarrow x\in L$.

However, there exists families formulas of \textit{constant} depth that compute undecidable languages.
In this work, we restrict our attention to uniform formulas, 
that is family of formulas for which the description of the
$n$-input formula can be computed efficiently.
We first recall a usual definition of uniform formulas.
\begin{definition}[``Usual'' polylog-time uniform formulas]
	A family of formulas $(\varphi_n)_{n \ge 1}$ of depth $(c + o(1))\log n$ 
	is \textit{polylog-time uniform} if there exists a machine $A_\varphi$
	such that for every $n$ and every $b\in\bit^{\leq (c + o(1))\log n}$,
	$A_\varphi(b, n)$ outputs a description of the gate at position $b$ in $\varphi_n$ in time $\log^{O(1)} n$.
\end{definition}

@@

\subsection{Details of the model}
Given an integer $k$ and a real $c$, we define the following interger linear program $P_{c,k}$ as follows:
\begin{equation}
	todo
\end{equation}
\todoh{describe model}
\todoh{link to code?}
